\section{Discussion \& Conclusion}
\label{sec:Conclusion}

The study shows that the right choice of dispatching algorithm for an AMoD system does not only have a strong impact on the performance in terms of waiting times for the customer but also that it bears a substantial economic advantage for the
operator. He is able to attract more customers through quicker pickups and lower prices than a competitor with only little investment.

In order to assess the significance for real fleets of (not necessarily
automated) taxis it needs to be noted that all of the presented algorithms are able to process dispatching and rebalancing tasks for fleets of thousands of vehicles within minutes. It is perfectly feasible to control 100k vehicles in five minute updates using a standard laptop for the computational tasks.

For the presented simulations, this still poses a burden, though,  because there a speedup compared to the reality of around one thousand times is desired to be able to run large numbers of simulations with different parameters. Hence, the algorithms
could only be tested on a subsample of 1\% of the agent population that is available. In future studies effort will be put into overcoming these restrictions, either by finding approximate formulations for the presented algorithms or pursuing research on completely new algorithms.

Throughout the paper, a ``100\%'' demand scenario has been used, in which all trips that possibly could be undertaken by AV were converted to the automated mode. The MATSim framework, however, offers the possibility to explicitly simulate attitudes toward new elements in the traffic system by defining utilities for using specific modes with a distinct valuation of travel costs, travel times and distances. This way, by integrating the presented algorithms into the full MATSim loop as shown in \cite{horl_abmtrans17} the actual attractiveness of an AV service could be analyzed including the tradeoff that people make between paying for the service, spending time in the vehicle and having to wait for it.
Naturally, not 100\% of possible trips would actually be performed by AV, but only a fraction. In such a scenario, also if maybe more remote areas would be included, completely different properties of an AV fleet control algorithm would be of interest, e.g. how well it is able to attract new customer groups in new regions by offering unproportionally low waiting times and make them stick to the service.
